SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-27 paper.tex
remove blue color

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions;
	\item legacy designs; and %, which are usually developed with low-level languages.
	\item \textcolor{blue}{support to different languages and interfaces};
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. \textcolor{blue}{Finally, the last one is related to the evolution of development processes and technologies, which may delay the application of suitable verification approaches.}

>>>>

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions;
	\item legacy designs; and %, which are usually developed with low-level languages.
	\item support to different languages and interfaces;
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. Finally, the last one is related to the evolution of development processes and technologies, which may delay the application of suitable verification approaches.
